A Poll-of-Polls Forecast for the 2024 U.S. Presidential Election: Analyzing Support Trends for Harris by Pollster and State

### 2024-11-04 paper/paper.qmd
refine the data section

# Plot the distribution of 'pct' using a histogram
ggplot(harris_data, aes(x = pct)) +
  geom_histogram(binwidth = 2, fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Percentage of Support (pct)",
       y = "Count")

@@

### Pollscore Measuring the Validity of Polling Questions

This variable was another factor we had put into consideration to check whether the validity of the polling questions affects the polling results. The 'pollscore' variable represents the score or reliability of the pollster in question. The numeric values are the error and bias that can be attributed to the pollster, which means negative numbers are better. @tbl-pollscore and @fig-pollscore suggests that while the majority of the polls are moderately to highly qualitative in the original dataset, a fraction of the polls with low-quality or no scores could add noise or uncertainty to the analysis.

```{r}
#| label: tbl-pollscore
#| tbl-cap: Summary statistics for the reliability scores of pollsters
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

summary_stats <- raw_elections_data %>%
  summarize(
    mean = round(mean(pollscore, na.rm = TRUE),2),
    median = round(median(pollscore, na.rm = TRUE),2),
    min = round(min(pollscore, na.rm = TRUE),2),
    max = round(max(pollscore, na.rm = TRUE),2),
    sd = round(sd(pollscore, na.rm = TRUE),2),
    n = n()
  )

```{r}
#| label: fig-pollscore
#| fig-cap: Distribution of the reliability scores of pollsters
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

# Distribution of 'pollscore' (bar plot) with simplified x-axis labels
ggplot(raw_elections_data, aes(x = factor(pollscore))) +
  geom_bar(fill = "skyblue", alpha = 0.7, color = "black") +
  theme_minimal() +
  scale_x_discrete(breaks = c(-1.5, -1, -0.5, 0, 0.5, 1, 1.5)) +  # Simplified labels at 0.5 intervals
  labs(x = "Pollscore",
       y = "Count")

After the filtering to polling data of high-quality polling organizations, we can find that the overall value and standard deviation of pollscores went down in @tbl-pollscore2. This implies that the polling data narrowed down to the responses from more reliable survey questions. @fig-pollscore2 also indicates that the data cleaning process effectively excluded less reliable sources, which can enhance the robustness of subsequent analyses.

```{r}
#| label: tbl-pollscore2
#| tbl-cap: Summary statistics for the reliability scores of high-quality pollsters in the analysis data
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

summary_stats <- harris_data %>%
  summarize(
    mean = round(mean(pollscore, na.rm = TRUE),2),
    median = round(median(pollscore, na.rm = TRUE),2),
    min = round(min(pollscore, na.rm = TRUE),2),
    max = round(max(pollscore, na.rm = TRUE),2),
    sd = round(sd(pollscore, na.rm = TRUE),2),
    n = n()
  )

```{r}
#| label: fig-pollscore2
#| fig-cap: Distribution of the reliability scores of high-quality pollsters in the analysis data
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

# Distribution of 'pollscore' (bar plot)
ggplot(harris_data, aes(x = factor(pollscore))) +
  geom_bar(fill = "skyblue", alpha = 0.7, color = "black", width = 0.5) +
  theme_minimal() +
  labs(x = "Pollscore",
       y = "Count")

>>>>

# Plot the distribution of 'pct' using a histogram
ggplot(harris_data, aes(x = pct)) +
  geom_histogram(binwidth = 1.5, fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Percentage of Support (pct)",
       y = "Count")

@@
